ATHENS course on Extreme-Value Theory

### 2022-03-16 Practicals/multivariate2022.Rmd
correction for rgl

First, we load the required R packages. 
```{r load packages, message=FALSE}
#library containing the pairwise beta angular measure:
library(BMAmevt)
#library for "3D Visualization Using OpenGL":
options(rgl.useNULL = TRUE)
options(rgl.printRglwidget = TRUE)
library(rgl)
```

```{r, echo=TRUE}
n=200
pars=c(0.5,0.2,0.2,6)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))

pars=c(.1,10,10,10)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)

pars=c(25,10,10,10)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)

pars=c(.1,.1,.1,.1)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)

pars=c(25,.1,.1,.1)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)
```

>>>>

First, we load the required R packages. 
```{r load packages, message=FALSE}
#library containing the pairwise beta angular measure:
library(BMAmevt)
#library for "3D Visualization Using OpenGL":
library(rgl)
```

```{r, echo=TRUE}
n=200
pars=c(0.5,0.2,0.2,6)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
rglwidget()

pars=c(.1,10,10,10)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)
rglwidget()

pars=c(25,10,10,10)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)
rglwidget()

pars=c(.1,.1,.1,.1)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)
rglwidget()

pars=c(25,.1,.1,.1)
w=rpairbeta(n,dimData=3,par=pars)
plot3d(w,xlab=expression(w[1]),ylab=expression(w[2]),zlab=expression(w[3]))
segments3d(c(1,0),c(0,1),c(0,0),col="blue")
segments3d(c(1,0),c(0,0),c(0,1),col="blue")
segments3d(c(0,0),c(0,1),c(1,0),col="blue")
points3d(0,0,0,col="blue",size=10)
rglwidget()
```
